---
title: "Milestone7"
author: "Feven Yohannes"
date: "April 17, 2020"
output: html_document
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(readr)
library(dplyr)
library(lmtest)
library(tinytex)

#Need this to run coeftest

library(sandwich)

#Need this to run vcovHc

library(tidybayes)

#Need this to make my graphic for my extension 

library(rstanarm)
library(cowplot)

#Need this for my graphics in my extension

library(stargazer)
library(tidyverse)

#Reading in the data 

budget <- read_csv("dataverse_files/replication_file_jop/data/budget_results.csv", col_types = cols(
  .default = col_double(),
  kab.x = col_character(),
  kab.y = col_character()
))

constituency_data  <- read_csv("dataverse_files/replication_file_jop/data/pub_opinion_results.csv",
                           col_types = cols(
  .default = col_double(),
  dapil = col_character()
                           ))

candidate_data  <- read_csv("dataverse_files/replication_file_jop/data/candidate_2019_data.csv",
                           col_types = cols(
  .default = col_double(),
  dapil = col_character()
                           ))

center_data  <- read_csv("dataverse_files/replication_file_jop/data/center_data.csv",
                           col_types = cols(
  .default = col_double(),
  dapil = col_character()
                           ))

gender_data  <- read_csv("dataverse_files/replication_file_jop/data/dapil_gender_composition.csv",
                           col_types = cols(
  .default = col_double(),
  dapil = col_character()
                           ))

election_data  <- read_csv("dataverse_files/replication_file_jop/data/election_characteristics_balance.csv",
                           col_types = cols(
  .default = col_double(),
  dapil = col_character()
                           ))

gender_estimation_data  <- read_csv("dataverse_files/replication_file_jop/data/estimation_sample_dapils_w_gender.csv",
                           col_types = cols(
  .default = col_double(),
  dapil = col_character()
                           ))
  
laws_data  <- read_csv("dataverse_files/replication_file_jop/data/laws_dprd_2009.csv",
                           col_types = cols(
  .default = col_double(),
  dapil = col_character()
                           ))

public_opinion_individual_data  <- read_csv("dataverse_files/replication_file_jop/data/pub_opinion_results_individual.csv",
                           col_types = cols(
  .default = col_double(),
  dapil = col_character()
                           ))
```

#Extension: 

```{r,extension for table1,results="asis", warning=FALSE}
set.seed(9)

#Instead of running the regression by using lm, I will use stan_lm
#Adding refresh=0 so it doesn't run multiple times
#Using prior=NULL because we have no prior since we are transforming te orginial lm regressions into a Bayesian model

mod_fem1_new <- stan_lm(v744a_f2012 ~ woman_win, data = constituency_data, prior= NULL, refresh=0)
mod_fem2_new <- stan_lm(v744b_f2012 ~ woman_win, data = constituency_data, prior= NULL,refresh=0)
mod_fem3_new <- stan_lm(v744c_f2012 ~ woman_win, data = constituency_data, prior= NULL,refresh=0)
mod_fem4_new <- stan_lm(v744d_f2012 ~ woman_win, data = constituency_data, prior= NULL,refresh=0)
mod_fem5_new <- stan_lm(v744e_f2012 ~ woman_win, data = constituency_data,prior= NULL,refresh=0)

#This added an index of the prior information onto the table

mod_fem7_new <- stan_lm(add_index_f2012 ~ woman_win, data = constituency_data, prior= NULL)

#Nobs computes the number of non-missing observations

observations_new <- c(nobs(mod_fem1_new),nobs(mod_fem2_new),nobs(mod_fem3_new),nobs(mod_fem4_new),nobs(mod_fem5_new),nobs(mod_fem7_new))

#Coefests is an inference for estimated coefficents on the models
#I need different names for the coeftests and the regressions bc my graphics will just be looking at bayesian regressions

mod_fem1_new_coef <- coeftest(mod_fem1_new)
mod_fem2_new_coef <- coeftest(mod_fem2_new)
mod_fem3_new_coef <- coeftest(mod_fem3_new)
mod_fem4_new_coef<- coeftest(mod_fem4_new)
mod_fem5_new_coef <- coeftest(mod_fem5_new)
mod_fem7_new_coef <- coeftest(mod_fem7_new)

#Made the models with their respective coefficents into a table 

table_new <- list(mod_fem1_new, mod_fem2_new, mod_fem3_new, mod_fem4_new, mod_fem5_new, mod_fem7_new)

note_text <- paste("Beta coefficients from OLS regression. Standard errors were calculated using the huber-white (HC0) correction. The outcomes are drawn from a battery of questions that asked respondents if it was acceptable to beat one's wife if she: (1) goes out without telling her husband; (2) neglects her children; (3) argues with her husband; (4) refuses sex; (5) burns the food. The index is an additive measure.")

#Used stargazer to make the table
#Using the outlined code from the paper

table_new = stargazer(table_new,
                  title = "Effect of Female Incumbency on Female Attitudes Towards IPV", 
                  label = 'tab:table_female',
                  model.names = F,
                  model.numbers = T,
                  #column.separate = c(6),
                  column.labels = c("Goes out", "Neglects children", "Argues", "Refuses sex", "Burns food", "Index"),
                  
                  multicolumn = T,
                  dep.var.labels = c("Is it okay to beat one's wife if she:"), 
                  add.lines = list(c("Observations", observations_new),
                                   c('Bandwidth', rep(c('1\\%'), 6))),
                  covariate.labels = c("Female Incumbency"),
                  star.cutoffs = c(0.05, 0.01),
                  #float.env = 'sidewaystable',
                  keep.stat = c("n"),
                  notes = NULL,
                  notes.align = 'l')

#I used overlap to put in the latec code to see the output
#ppcheck >>> shows difference between the  model data... how well the bayesian regression fits with the data that is provided 
#dark line is the data, light line is the bayesian model


model1_check <- pp_check(mod_fem1_new,"dens_overlay") +
  labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in female attitudes on one's acceptance of beating a wife if she goes out")
model2_check <- pp_check(mod_fem2_new,"dens_overlay") +
  labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in female attitudes on one's acceptance of beating a wife if she neglects her children")
model3_check <- pp_check(mod_fem3_new,"dens_overlay") +
  labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in female attitudes on one's acceptance of beating a wife if she argues")
model4_check <- pp_check(mod_fem4_new,"dens_overlay") +
  labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in female attitudes on one's acceptance of beating a wife if she refuses sex")
model5_check <- pp_check(mod_fem5_new,"dens_overlay") +
  labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in female attitudes on one's acceptance of beating a wife if she burns food")

#This graph just looks at the index showing overall IPV attitude changes

model7_check <- pp_check(mod_fem7_new,"dens_overlay") +
  labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in overall female attitudes on Intimate Partner Violence")

#Arranging all of the graphs on one page

graphic1 <- plot_grid(model1_check,model2_check,model3_check,model4_check,model5_check,model7_check)
```


```{r,extension for table2, making my graphic,results="asis",warning=FALSE}
set.seed(9)

#These lines of code do the same thing that the previous table did, however, rather than predicting female respondent results, it predicts male respondent results. 

#Instead of running the regression by using lm, I will use stan_lm
#Adding refresh=0 so it doesn't run multiple times
#Using prior=NULL because we have no prior since we are transforming te orginial lm regressions into a Bayesian model

mod_mal1_new <- stan_lm(v744a_m2012 ~ woman_win, prior= NULL, data = constituency_data,refresh=0)
mod_mal2_new <- stan_lm(v744b_m2012 ~ woman_win, prior= NULL, data = constituency_data,refresh=0)
mod_mal3_new <- stan_lm(v744c_m2012 ~ woman_win, prior= NULL, data = constituency_data,refresh=0)
mod_mal4_new <- stan_lm(v744d_m2012 ~ woman_win, prior= NULL, data = constituency_data,refresh=0)
mod_mal5_new <- stan_lm(v744e_m2012 ~ woman_win,  prior= NULL,data = constituency_data,refresh=0)
mod_mal7_new <- stan_lm(add_index_m2012 ~ woman_win,  prior= NULL,data = constituency_data,refresh=0)

#Named it observations2_new, so I didn't get confused with the other names

observations2_new <- c(nobs(mod_mal1_new),nobs(mod_mal2_new),nobs(mod_mal3_new),nobs(mod_mal4_new),nobs(mod_mal5_new),nobs(mod_mal7_new))

#The code below takes the coeftest of the models. I got rid of the original code that included covariance bc the covariance isn't present when running stan_lm, althogh it is in the original code when we ran stan_lm

mod_mal1_coef <- coeftest(mod_mal1_new)
mod_mal2_coef <- coeftest(mod_mal2_new)
mod_mal3_coef <- coeftest(mod_mal3_new)
mod_mal4_coef <- coeftest(mod_mal4_new)
mod_mal5_coef <- coeftest(mod_mal5_new)
mod_mal7_coef <- coeftest(mod_mal7_new)

table_new_male <- list(mod_mal1_new, mod_mal2_new, mod_mal3_new, mod_mal4_new, mod_mal5_new, mod_mal7_new)

note_text <- paste("Beta coefficients from OLS regression. Standard errors were calculated using the huber-white (HC0) correction. The outcomes are drawn from a battery of questions that asked respondents if it was acceptable to beat one’s wife if she: (1) goes out without telling her husband; (2) neglects her children; (3) argues with her husband; (4) refuses sex; (5) burns the food. The index is an additive measure.")

table_new_male = stargazer(table_new_male,
                  title = "Effect of Female Incumbency on Male Attitudes Towards IPV",
                  label = 'tab:table_male',
                  model.names = F,
                  model.numbers = T,
                  #column.separate = c(6),
                  column.labels = c("Goes out", "Neglects children", "Argues", "Refuses sex", "Burns food", "Index"),
                  
                  multicolumn = T,
                  dep.var.labels = c("Is it okay to beat one's wife if she:"), 
                  add.lines = list(c("Observations", observations2_new),
                                   c('Bandwidth', rep(c('1\\%'), 6))),
                  covariate.labels = c("Female Incumbency"),
                  star.cutoffs = c(0.05, 0.01),
                  #float.env = 'sidewaystable',
                  keep.stat = c("n"),
                  notes = NULL,
                  notes.align = 'l')

model1_check_male <- pp_check(mod_mal1_new,"dens_overlay") +
labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in male attitudes on one's acceptance of beating a wife if she goes out")
model2_check_male <- pp_check(mod_mal2_new,"dens_overlay") +
   labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in male attitudes on one's acceptance of beating a wife if she neglects her children")
model3_check_male <- pp_check(mod_mal3_new,"dens_overlay") +
labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in male attitudes on one's acceptance of beating a wife if she argues")
model4_check_male <- pp_check(mod_mal4_new,"dens_overlay") +
 labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in male attitudes on one's acceptance of beating a wife if she refuses sex")
model5_check_male <- pp_check(mod_mal5_new,"dens_overlay") +
   labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in male attitudes on one's acceptance of beating a wife if she burns food")

#This graph just looks at the index showing overall IPV attitude changes for males

model7_check_male <- pp_check(mod_mal7_new,"dens_overlay") +
  labs(title = "Posterior Predictive Checking",subtitle = "Examining the regression that predicts the change in overall male attitudes on Intimate Partner Violence")

graphic2 <- plot_grid(model1_check_male,model2_check_male,model3_check_male,model4_check_male,model5_check_male,model7_check_male)

```

For my extension, I focused on re-creating the original regressions through a Bayesian method rather than a standard linear regression. I ran two models from the main results of the paper. The first was the model that predicted female attitude changes on IPV public opinion. The second was a similiar model that predicted male attitudes on IPV public opinion. These new models used the Bayesian inference for linear modeling and thus included regularizing piors on the model parameters. Overall, I attempted to examine any discrepencies between the results of these models with the original models found in the paper. 

In my first model, the model that predicited the change in female IPV opinions, the results between the coefficents of the standard linear model was consistent with the  Bayesisan model. The coefficents for female incumbency, which measured the change in public opinion for regions where a female candidate won by one percentage point. The results essentially rendered the same output for each dependent variable after accounting for some unavoidable discrpencies for error (these discrpencies were very minor).For example we see that the coefficents for Female Incumbency on the second dependent variable in the orginal paper is -.0.058. In the new model we see the Female Incumbency coefficent at around -0.0366. Thus, although there is a difference of almost two percent, we can include that these results are quite consistent.Similiar to the first model that predicted the change in IPV opions, the second model predicted the change in male IPV opinions. While running these regressions, I also found that the modeling that I had ran with the Bayesian method was consistent with the modeling from the original paper. 

In addition to the models that I created, I also ran a posterior predictive check on each regression for both the models that predicted the change in female and male attitudes. The graphics that I have shown below represent these posterior predictive checkings, a method that simulates replicated data and compares it to the orginal data. Each graph compares the simulated data which is donoted as yrep and has a light blue color, with the orginal data which is donoted as y and has a dark blue color. When running the posterior predictive check on the regressions that predicted female public opinion, we can see that both fitted lines are quite similiar. This suggests that the model that we have is a pretty good fit for our data. However, when running the posterior predicitve check on regressions that predicted male public opinion, we can see that that fitted lines have more variance and at times don't follow the same pattern. This is specifally true for regressions that predicted male opinions from the third, fourth, and fifth dependent variable. This outcome is in line with the results of the data, as the paper stated that the regressions for males show less signifcant results, thus hinting that the models are not a great fit for the data. 

Github repo: https://github.com/fyohannes/Milestone7
